---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# prcbench

The aim of `prcbench` is to provide a testing workbench for evaluating 
Precision-Recall curves under various conditions. It contains integrated 
interfaces for the following five different tools as well as predefined test 
data sets. 

| Tool          | Link                                                     |
| ------------- | -------------------------------------------------------- |
| ROCR          | [CRAN](https://cran.r-project.org/package=ROCR)     |
| AUCCalculator | [Web site](http://mark.goadrich.com/package=AUC)        |
| PerfMeas      | [CRAN](https://cran.r-project.org/package=PerfMeas) |
| PRROC         | [CRAN](https://cran.r-project.org/package=PRROC)    |
| precrec       | [CRAN](https://cran.r-project.org/package=precrec)  |

## Installation
Only a development version of `prcbench` is currently available at 
[our GitHub repository](https://github.com/takayasaito/prcbench). 

To install it:

  1. Make sure you have a working development environment.
      * **Windows**: Install [Rtools](http://cran.r-project.org/bin/windows/Rtools/).
      * **Mac**: Install Xcode from the Mac App Store.
      * **Linux**: Install a compiler and various development libraries (details vary across different flavors of Linux).

  2.  Install required Bioconductor packages for `PerfMeas`.
```
## try http:// if https:// URLs are not supported
source("https://bioconductor.org/biocLite.R")
biocLite("limma")
biocLite("graph")
biocLite("RBGL")
```
  3.  Install `devtools` from CRAN with `install.packages("devtools")`.

  4.  Install `prcbench` from the GitHub repository with `devtools::install_github("/takayasaito/prcbench")`

## Documentation
A package vignette - Introduction to prcbench - contains the descriptions of the functions with several useful examples. View the vignette with `vignette("introduction", package = "prcbench")`.

In addition, all the main functions have their own help pages with examples.

## Examples

Following two examples show the basic usage of `prcbench` functions.

### Benchmarking

The `run_benchmark` function outputs the result of [microbenchmark](https://cran.r-project.org/package=microbenchmark) for 
specified tools.
```{r}
## Load library
library(prcbench)

## Run microbenchmark for aut5 on b10
testset <- create_testset("bench", "b10")
toolset <- create_toolset(set_names = "auc5")
res <- run_benchmark(testset, toolset)

## Use knitr::kable to show the result in a table format
knitr::kable(res$tab, digits = 2)
```

### Evaluation of Precision-Recall curves
The `run_evalcurve` function evaluates Precision-Recall curves with predefined
test datasets. The `autoplot` shows a plot with the result of the 
`run_evalcurve` function.

```{r, warning=FALSE}
## ggplot2 is necessary to use autoplot
library(ggplot2)

## Plot base points and the result of precrec on c1, c2, and c3 test sets
testset <- create_testset("curve", c("c1", "c2", "c3"))
toolset <- create_toolset("precrec")
scores1 <- run_evalcurve(testset, toolset)
autoplot(scores1)

## Plot the results of PerfMeas and PRROC on c1, c2, and c3 test sets
toolset <- create_toolset(c("PerfMeas", "PRROC"))
scores2 <- run_evalcurve(testset, toolset)
autoplot(scores2, base_plot = FALSE)
```


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
